### 2022-11-13 chapter1.tex
Realignment figure now uses new version and caption

\begin{figure}[h!]
\includegraphics[width=\textwidth]{realignment/out/23D9_A.png}
\includegraphics[width=\textwidth]{realignment/out/23D9_B.png}
\centering
\caption{\textbf{Alignment with long poorly supported segments.}
The alignments of representative sequences in orthologous group 23D9 are shown before (panel A) and after (panel B) refinement. The refinement process removes long poorly supported segments at the termini. However, if residues are aligned to consensus columns before and after a long poorly segment, it remains in the alignment.}
\label{fig:realignment}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{realignment/out/merged.png}
\centering
\caption{\textbf{Alignment with long poorly supported segments.}
The alignments of representative sequences in orthologous groups 23D9 (A), 01E0 (B), and 07C3 (C) are shown before and after refinement. The refinement process removes long poorly supported segments at the termini. However, if residues are aligned to consensus columns before and after a long poorly segment, it remains in the alignment.}
\label{fig:realignment}
\end{figure}
